### 2021-08-09 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
comments and edits

\subsection{Cycle Component Modeling}
%======================================================================================
Components present in the cycles are modeled using various techniques. Turbines and compressors are analyzed using isentropic efficiencies. Counter flow heat exchangers use the effectiveness-NTU method while black box heat exchangers use a simple energy balance for state point calculations. The lead-cooled fast reactor is assumed to be a black box heat exchanger because of the constant heat input and state points on the sCO$_2$ inlet and outlet are provided. The concentrating solar power cycle is modeled with necessary components including hot and cold TES, reciever, pumps and counter flow heat exchangers.

@@

The modeled cycles have a number of compressors and turbines. The turbines and compressors are modeled for each cycle using constant isentropic efficiency values summarized in Table \ref{tab-cycle-constants}. Turbines take the high pressure sCO$_2$ and expand it through a series of blades allowing a production of energy, while compressors input mechanical energy to increase the pressure of the sCO$_2$. The turbines and compressors are assumed to be at steady state, exchange no heat with the surroundings, and have a single inlet and outlet. Power calculations are initially done on ideal, reversible compressors or turbines then are scaled by the isentropic efficiencies to provide an estimate for a realizable component. Using this estimate, along with a known low and high side pressures, temperature and enthalpy outlets of the turbine and compressor can be calculated \cite{klein_nellis_2011}.

@@

Black box heat exchangers are simplified heat exchangers which have no approach temperature or pinch point. These heat exchangers use an energy balance with mass flow inlet energy, heat input or output, and mass flow outlet energy. The energy balance equation used for all black box heat exchangers is Equation \ref{eq-black}.

\begin{equation}
    \label{eq-black}
    \dot{m}_{in}*h_{in} + \dot{Q}_{in} = \dot{m}_{out}*h_{out} + \dot{Q}_{out},
\end{equation}

In this equation the energy input to the system is on the left hand side with $\dot{m}_{in}$ multiplied by $h_{in}$ being energy from the mass flow and $\dot{Q}_{in}$ being heat transfer directly to the flow from an outside source. The right hand side of the equation is heat leaving the energy balance. The mass flow leaving is $\dot{m}_{out}$ with enthalpy of $h_{out}$ and $\dot{Q}_{out}$ is the heat transfer leaving from the flow. Black box energy balances are used in three situations, the Reciever, LFR HX, and PC HX. These heat exchangers are not exchaustively modeled because the state points on the inlet and outlet are constrained by design parameters.

Counter flow heat exchangers are modeled with two fluids flowing in opposite directions exchanging heat from the hot side to the cold side. The temperatures of the hot and cold flows on either side of the the heat exchanger have a temperature difference known as an approach temperature. A diagram showing a simplified example of a counterflow heat exchanger is illustrated in Figure \ref{counter-flow-hx}.

@@

Additional assumptions of the counter flow heat exchanger model are no heat loss to the surroundings, $\dot{Q}_{surr}$ is zero, and no pressure drops accross the heat exchangers. Counter flow heat exchanger calculations require two known state points, fluid libraries, mass flow rate of hot and cold side, and a specified approach temperature. In all of the modeled cases, the approach temperature is set to a value of 10 K. The fluid libraries referenced are built into EES for Carbon Dioxide and Salt(60\% NaNO3 40\% KNO3) \cite{pacheco_1995_salt_properties,roland_1996_co2_properties}.

@@

\begin{equation}
    \label{eq-lfr-black-box}
    \dot{m}_{inlet}*h_{inlet} + \dot{Q}_{LFRHX} = \dot{m}_{outlet}*h_{outlet},
\end{equation}

Where the left hand side, $\dot{m}_{inlet}$, $h_{inlet}$, and $\dot{Q}_{LFRHX}$, is the energy into the flow and the right hand side, $\dot{m}_{outlet}$ and $h_{outlet}$, is the energy brought out from the flow of sCO$_2$. The amount of energy transfered into the cycle, $\dot{Q}_{LFRHX}$, is set at 950 MW, and outlet temperature of the sCO$_2$ from the LFR HX is set at a value of 595$^{\circ}$C. The outlet temperature of the LFR is rigid due to high temperature material limits on the LFR lead side. Low sCO$_2$ LFR inlet temperature has a lower limit of 340$^{\circ}$C and an optimal value of 400$^{\circ}$C. Increasing this temperature above this optimal value leads to diminishing returns on the LFR efficiency.

@@

The CSP salt cycle modeled in this paper is composed of hot and cold thermal energy storage (TES), pumps, receiver, sCO$_2$-to-Salt counter flow heat exchanger (C2S), and CSP counter flow heat exchanger (CSP HX). The diagram for this CSP salt cycle is seen in Figure \ref{csp}.

\end{paracol}
%MW: Best practice is to allow figures to float. To do this, specify the location as [htb] ("here, top, or bottom"). I've done a search-replace for all figures to do this. 
\begin{figure}[htb] 
    \widefigure
    \includegraphics[width=10 cm]{Definitions/csp.pdf}
    \caption{Diagram for CSP cycle with cold and hot thermal energy storage, pumps, and csp black box heat input\label{csp}}
\end{figure}
\begin{paracol}{2}
\linenumbers
\switchcolumn

The CSP salt cycle uses 60\% sodium nitrate and 40\% potassium nitrate 'solar salt' as the heat transfer fluid. Solar salt stored in the hot TES can be dispatched on demand through the CSP HX when grid demand increases and held when grid demand is low. Current CSP salt cycles heat solar salt with receivers and store it in hot TES tanks at 565$^{\circ}$C. Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to 720$^{\circ}$C, but due to high temperature limitations with the LFR outlet, the hot TES temperature is set at 595$^{\circ}$C for all modeled cycles \cite{mehos2017concentrating}. The cold TES temperature takes on three different values according to cycle configuration capabilitites: 390$^{\circ}$C, 410$^{\circ}$C, and 440$^{\circ}$C. In addition to the lower hot TES temperature, current CSP salt cycles lack a secondary option for charging the hot TES \cite{hamilton2020dispatch}. The studied CSP salt cycle has two TES charging options: a receiver, which generates heat from a heliostat field, and C2S heat exchanger, which draws excess heat from the sCO$_2$ Brayton cycle. It is assumed that only one hot TES charging option can be active at any given time.

The C2S heat exchanger is active during the 'charging' cycle configurations, when the focus is on heat storage for later use. During this process there is no solar salt flow through the receiver. Pump 1 is active moving solar salt from cold TES to hot TES through the C2S heat exchanger, which is extracting heat from the sCO$_2$ Brayton cycle.

'Non-charging' cycle configurations has the receiver charging the hot TES, C2S heat exchanger is not transfering heat, and the LFR is dispatching energy directly into electrical generation. When electrical generation is occuring, the heat input in this cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 7.5e8 W from the heliostat field. The hot storage is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle to be converted into electricity. The cooled salt is stored in cold storage and moved through Pump 2 where the heat addition from the receiver is added.

\subsection{Generalization of Cycle Modeling}
%======================================================================================

The cycles presented are generalized in order to draw a more direct comparison. The generalized parameters include isentropic efficiencies, heat exchanger approach temperatures, pressures, heat input, and pump constants. These values are summarized in Table \ref{tab-cycle-constants}.

%MW: Also changing the specialtable position to allow latex to better place tables.
\begin{specialtable}[htbp] 
    \caption{Constant cycle parameters with definition, variable and set value. \label{tab-cycle-constants}}
    \begin{tabular}{lcc}
    \toprule
    \textbf{Parameter} & \textbf{Variable}	& \textbf{Design Point Value}\\
    \midrule
    \textit{Efficiencies}\\
    Main Compressor & $\eta_{MC}$		& 0.91 (-)\\
    Re-Compressor & $\eta_{RC}$		& 0.89 (-)\\
    Turbine & $\eta_{T}$		& 0.90 (-)\\
    Pump & $\eta_{P}$      & 0.90 (-)\\
    \midrule
    \textit{Approach Temperatures}\\
    Low Temperature Recuperator & $\delta_{LTR}$		& 10 (K)\\
    High Temperature Recuperator & $\delta_{HTR}$		& 10 (K)\\
    Concentrating Solar Power Heat Exchanger & $\delta_{CSPHX}$	& 10 (K)\\
    \midrule
    \textit{Pressures}\\
    Pressure Ratio & $PR$ & 3.27 (-)\\
    High Side Pressure & $P_{2A}$ & 2.88e7 (Pa)\\
    \midrule
    \textit{Heat Into System}\\
    Lead-Cooled Fast Reactor Heat Transfer & $\dot{Q}_{LFRHX}$ & 9.5e8 (W)\\
    Concentrating Solar Power Heat Transfer & $\dot{Q}_{CSP}$ & 7.5e8 (W)\\
    \midrule
    \textit{Temperature}\\
    Main Compressor Inlet & $T_{1A}$ & 313.2 (K)\\
    %Lead-Cooled Fast Reactor sCO$_{2}$ Low Temperature & $T_{4}$,$T_{1C}$,$T_{5A}$,$T_{4C}$ & 673.2 (K)\\
    Lead-Cooled Fast Reactor sCO$_{2}$ High Temperature & $T_{5}$,$T_{2C}$,$T_{6A}$,$T_{5C}$ & 868.2 (K)\\
    \midrule
    \textit{Pumps}\\
    Pressure Rise Across Pump & $\Delta_{P}$ & 3.726e6 (Pa)\\
    Pump Low Side Pressure & $P_{S5-B}$ & 3.0e6 (Pa)\\ 
    \bottomrule
    \end{tabular}
\end{specialtable}

@@

In addition to generalized parameters, all cycles have identical recompression sides. The recompression side contains a PreCooler, Low Temperature Recuperator, and two compressors; Main Compressor and ReCompressor.

@@

\begin{specialtable}[H] 
    \caption{Summary of all modeled non-charging and charging cycles with descriptions. \label{tab-cycle_sum}}
    \begin{tabular}{ll}
    \toprule
    \textbf{Cycle Label} & \textbf{Description}\\
    \midrule
    \textit{Non-Charging}\\
    C-LFR-ON & Two-cycle configuration with LFR as heat source.\\
    C-CSP-ON & Two-cycle configuration with CSP as heat source.\\
    C-1HTR1T-ON & CSP and LFR heat sources in parallel with one turbine.\\
    C-2HTR3T-ON & Seperatre CSP and LFR loops each with dedicated HTR and turbine.\\
    \midrule
    \textit{Charging}\\
    C-LFR-PRE & Turbine is prior to the SALT HX.\\
    C-LFR-POST & Turbine is after the SALT HX.\\
    C-LFR-PAR & Turbine is parallel to the SALT HX.\\
    C-LFR-CIRC & Circulator bridges the LFR and SALT HX.\\
    \bottomrule
    \end{tabular}
\end{specialtable}

@@

The numerator in Equation \ref{eq-eta-cycle} is the Alternator power, or the power produced from the turbines, $\dot{W}_{T}$, minus the required power of the compressors, $\dot{W}_{MC}$ and $\dot{W}_{RC}$. The denominator is the total power input into the system from the LFR HX, $\dot{Q}_{LFRHX}$, and CSP HX, $\dot{Q}_{CSPHX}$.

@@

The two-cycle configuration that is tested has independent sCO$_{2}$ loops bridged by a CSP cycle. This cycle has two sCO$_{2}$ Brayton Cycles: C-LFR-ON and C-CSP-ON. Configuration of components for these two cycles is identical with the exception of heat inputs. C-LFR-ON has heat provided from a LFR while C-CSP-ON has heat provided from the CSP. These two cycles individually operate when the focus of plant operation is primarily electricity generation.

The cycle that is using the LFR heat input in the two-cycle configuration is labeled as C-LFR-ON and the cycle diagram is illustrated in Figure \ref{c-lfr-on}.

\end{paracol}
\begin{figure}[H] 
    \widefigure
    \includegraphics[width=\linewidth]{Definitions/c-lfr-on.pdf}
    \caption{Diagram for C-LFR-ON with focus on electricity generation\label{c-lfr-on}}
\end{figure}
\begin{paracol}{2}
\linenumbers
\switchcolumn

Two seperate sensitivity studies on the LFR inlet temperature are completed for C-LFR-ON. The unconstrained study is performed by gradually increasing the mass flow to the main compressor while maximizing cycle efficiency. The constrained study is calculated by setting the LFR inlet temperature to the design value of 673.2 K (400$^{\circ}$C), which is a requirement of the LFR primary circuit to maximize power output within material limits.
%BL: flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint

The cycle that is using the CSP heat input in the two-cycle configuration is labeled C-CSP-ON and the cycle diagram is shown in Figure \ref{c-csp-on}.

\end{paracol}
\begin{figure}[H] 
    \widefigure
    \includegraphics[width=\linewidth]{Definitions/c-csp-on.pdf}
    \caption{Diagram for C-CSP-ON with focus on electricity generation\label{c-csp-on}}
\end{figure}
\begin{paracol}{2}
\linenumbers
\switchcolumn

@@

%BL: be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from

\end{paracol}
\begin{figure}[H] 
    \widefigure
    \includegraphics[width=\linewidth]{Definitions/c-1htr1t-on.pdf}
    \caption{Diagram for C-1HTR1T-ON with focus on electricity generation\label{c-1htr1t-on}}
\end{figure}
\begin{paracol}{2}
\linenumbers
\switchcolumn

In this cycle, the LFR HX and CSP HX have identical inlet temperatures due to splitting the flow prior to their parallel orientation. Therefore, three sensitivity studies are done on the C-1HTR1T-ON EES model. The initial two studies have the low LFR temperature constrained to the value of 673.2 K with varied cold CSP TES and maximized cycle efficiency. The two tested values for cold CSP TES with constrained LFR low temperature are 683.2 K and 713.2 K. The desired cold CSP TES temperature of 663.2 K is not possible with the constraint on the LFR low temperature (because it cannot be colder than the sCO$_2$ that removes heat from the salt). In this case, to obtain the desired cold CSP TES temperature, the constraint on the LFR low temperature is removed, droping the temperature of the LFR inlet to 653.2 K. 
%BL: I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets. Asp you will want to explain the criteria that go into cold storage temp. Lower = more delta T = more dispatchability

@@

Mixing two different temperature flows before the turbine in a Brayton cycle has a negative effect on cycle efficiency. To quantify the reduction in cycle efficiency, another cycle with no mixing prior to the turbine is desired. This cycle, C-2HTR3T-ON, can be seen in Figure \ref{c-2htr3t-on} and has two high temperature recuperators and three turbines. The LFR is powering one turbine, T1, and recuperating heat through a dedicated high temperature recuperator, HTR1. The CSP cycle also contains two separate turbines, T2, while having a dedicated high temperature recuperator, HTR2. After the high temperature recuperators, the two flows are combined and sent to the LTR hot side. 
%BL: this is more about having a compromise option of intermediate complexity and efficiency

@@

Three sensitivity studies are done on the C-2HTR3T-ON model. Two with the LFR low temperature constrained and one without this constraint. The two constrained studies had varied cold CSP TES temperature with the lowest temperature of 663.2 K and highest temperature of 713.2 K. The unconstrained low LFR inlet study is calculated at a cold CSP TES temperature of 663.2 K.  
%BL: this is clearer than the previous one but bullets could still be useful

@@

Charging cycle configurations focus on an energy storage operating mode. These configurations test the optimal location of LFR heat extraction through the SALT HX. To maximize the available heat for extraction, alternator power is set to zero and turbine power is therefore equal to the compressors' demand. The excess energy from the LFR is thermally stored in the TES for later use when grid demand increases. Comparison of where thermal energy is extracted in the cycle is done by using the same Brayton cycle, C-LFR-ON, and configuring the salt heat exchanger in different locations around the turbine. To quantify the effectiveness of TES charging techniques a heat storage efficiency, $\eta_{heatstorage}$, is defined by Equation \ref{eq-eta-heatstorage}.
%BL: explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output

@@

Whereas $\dot{Q}_{S2C}$ is the amount of heat transfered through S2C and the addition of $\dot{Q}_{LFRHX}$ and $\dot{Q}_{CSPHX}$ is the total amount of heat input into the system from the LFR HX and CSP HX.

>>>>

% **************************************

%MW: I've fixed spelling in a few places. You can install a spell checker to highlight misspelled words. I use the "Code spell checker" extension.

\subsection{Cycle Component Modeling}
%======================================================================================
Components present in the cycles are modeled using various techniques \added{and are discussed in more detail below}. Turbines and compressors are analyzed using isentropic efficiencies. Counter flow heat exchangers use the effectiveness-NTU method while \added{simplified} ``black box'' heat exchangers use a simple energy balance for state point calculations. The lead-cooled fast reactor is assumed to be a black box heat exchanger because of the constant heat input and state points on the sCO$_2$ inlet and outlet are provided. The concentrating solar power cycle is modeled with necessary components including hot and cold TES, receiver, pumps and counter flow heat exchangers.

@@

\replaced{Turbines}{The modeled cycles have a number of compressors and turbines. The turbines} and compressors are modeled for each cycle using constant isentropic efficiency values \added{which are} summarized in Table \ref{tab-cycle-constants}. Turbines take the high pressure sCO$_2$ and expand it through a series of blades allowing a production of energy, while compressors input mechanical energy to increase the pressure of the sCO$_2$. The turbines and compressors are assumed to be at steady state, exchange no heat with the surroundings, and have single inlet and outlet \added{streams}. Power calculations are initially done on ideal, reversible compressors or turbines then are scaled by the isentropic efficiencies to provide an estimate for a realizable component.\mw{this is kind of an awkward way to describe what's happening. I think most readers are familiar with isentropic efficiencies and this can be omitted.} Using this estimate, along with a known low and high side pressures, temperature and enthalpy outlets of the turbine and compressor \replaced{are}{can be} calculated \cite{klein_nellis_2011}.

@@

Black box heat exchangers are simplified heat exchangers which have no approach temperature or pinch point. These heat exchangers use an energy balance with mass flow inlet energy, heat input or output, and mass flow outlet energy. The energy balance equation used for all black box heat exchangers is Equation \ref{eq-black}.\mw{This is for a single flow stream. Why would there be $\dot{Q}_{in}$ and $\dot{Q}_{out}$ in a single flow stream? Also, the variable should be consistent with the figure, which would be $\dot{Q}_{HX}$.}

\begin{equation}
    \label{eq-black}
    \dot{m}_{in}*h_{in} + \dot{Q}_{in} = \dot{m}_{out}*h_{out} + \dot{Q}_{out},
\end{equation}
\mw{Use the command ``\textbackslash cdot'' instead of asterisks to denote multiplication}

In this equation the energy input to the system is on the left hand side with $\dot{m}_{in}$ multiplied by $h_{in}$ being energy from the mass flow and $\dot{Q}_{in}$ being heat transfer directly to the flow from an outside source. The right hand side of the equation is heat leaving the energy balance. The mass flow leaving is $\dot{m}_{out}$ with enthalpy of $h_{out}$ and $\dot{Q}_{out}$ is the heat transfer leaving from the flow. Black box energy balances are used in three situations, the Receiver, LFR HX, and PC HX. These heat exchangers are not exhaustively modeled because the state points on the inlet and outlet are constrained by design parameters.

Counter flow \mw{I normally use ``counter-flow''} heat exchangers are modeled with two fluids flowing in opposite directions exchanging heat from the hot side to the cold side. The temperatures of the hot and cold flows on either side of the the heat exchanger have a temperature difference known as an approach temperature. A diagram showing a simplified example of a counter flow heat exchanger is illustrated in Figure \ref{counter-flow-hx}.

@@

Additional assumptions of the counter flow heat exchanger model are: no heat loss to the surroundings, $\dot{Q}_{surr}$ is zero, \mw{these are equivalent} and no pressure drops across the heat exchangers. Counter flow heat exchanger calculations require two known state points, fluid libraries, mass flow rate of hot and cold side, and a specified approach temperature. In all of the modeled cases, the approach temperature is set to a value of $10 K$.\mw{Justify} The fluid libraries referenced are built into EES for Carbon Dioxide and Salt(60\% NaNO3 40\% KNO3) \cite{pacheco_1995_salt_properties,roland_1996_co2_properties}.

@@

\begin{equation}
    \label{eq-lfr-black-box}
    \dot{m}_{inlet}*h_{inlet} + \dot{Q}_{LFRHX} = \dot{m}_{outlet}*h_{outlet},
\end{equation}
\mw{If mass is conserved, use a single $\dot{m}$}

Where the left hand side, $\dot{m}_{inlet}$, $h_{inlet}$, and $\dot{Q}_{LFRHX}$, is the energy into the flow and the right hand side, $\dot{m}_{outlet}$ and $h_{outlet}$, is the energy brought out from the flow of sCO$_2$. The amount of energy transferee into the cycle, $\dot{Q}_{LFRHX}$, is set at $950 MW$, and outlet temperature of the sCO$_2$ from the LFR HX is set at a value of 595$^{\circ}$C. 
\mw{Make sure numbers are in math mode}
The outlet temperature of the LFR is \replaced{specified, accounting for the}{rigid due to} high temperature material limits on the LFR lead side. Low sCO$_2$ LFR inlet temperature has a lower limit of 340$^{\circ}$C and an optimal value of 400$^{\circ}$C.
\mw{How do we know that 400C is the optimal temperature? This information is given to us by Westinghouse, right?} 
Increasing this temperature above this optimal value leads to diminishing returns on the LFR efficiency.

@@

The CSP salt cycle modeled in this paper is composed of hot and cold thermal energy storage (TES), pumps, receiver, sCO$_2$-to-salt counter flow heat exchanger (C2S), and CSP counter flow heat exchanger (CSP HX). The diagram for this CSP salt cycle is seen in Figure \ref{csp}.

\mw{Best practice is to allow figures to float. To do this, specify the location as [htb] ("here, top, or bottom"). I've done a search-replace for all figures to do this. }

% \end{paracol}

\begin{figure}[htb]

    \widefigure
    \includegraphics[width=10 cm]{Definitions/csp.pdf}
    \caption{Diagram for CSP cycle with cold and hot thermal energy storage, pumps, and csp black box heat input\label{csp}}
\end{figure}
% \begin{paracol}{2}
% \linenumbers
% \switchcolumn

The CSP salt cycle uses 60\% sodium nitrate and 40\% potassium nitrate 'solar salt' as the heat transfer fluid. Solar salt stored in the hot TES can be dispatched on demand through the CSP HX when grid demand increases and held when grid demand is low. Current CSP salt cycles heat solar salt with receivers and store it in hot TES tanks at 565$^{\circ}$C. Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to 720$^{\circ}$C, but due to high temperature limitations with the LFR outlet, the hot TES temperature is set at 595$^{\circ}$C for all modeled cycles \cite{mehos2017concentrating}. The cold TES temperature takes on three different values according to cycle configuration capabilities: 390$^{\circ}$C, 410$^{\circ}$C, and 440$^{\circ}$C. In addition to the lower hot TES temperature, current CSP salt cycles lack a secondary option for charging the hot TES \cite{hamilton2020dispatch}. The studied CSP salt cycle has two TES charging options: a receiver, which generates heat from a heliostat field, and C2S heat exchanger, which draws excess heat from the sCO$_2$ Brayton cycle. It is assumed that only one hot TES charging option can be active at any given time.

The C2S heat exchanger is active \replaced{in}{during} the 'charging' cycle configurations, when the focus is on heat storage for later use. During this process there is no solar salt flow through the receiver. \mw{Is this necessarily true? Couldn't there be a condition where we'd like to dump energy from the LFR while simultaneously collecting from CSP?} Pump 1 is actively moving solar salt from cold TES to hot TES through the C2S heat exchanger, which is extracting heat from the sCO$_2$ Brayton cycle.

'Non-charging' cycle configurations \replaced{are characterized by operations wherein}{has} the receiver is charging the hot TES, the C2S heat exchanger is not transferring heat, and the LFR is \replaced{heat}{dispatching energy} directly to generate electricity. When electrical generation is occurring, the heat input in this \mw{``this'' is ambiguous} cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 7.5e8 W from the heliostat field. The hot storage is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle to be converted into electricity. The cooled salt is stored in cold storage and moved through Pump 2 where the heat addition from the receiver is added.

\subsection{Generalization of Cycle Modeling}
%======================================================================================
\mw{What do you mean by ``generalized?''}

\mw{We need an overview here of our process for identifying which cycles will be modeled, as the discussion below gets a bit complicated with all of the different permutations. It might be helpful to have a model taxonomy that schematically shows how the different models are related to each other.}

\replaced{In order to draw a more direct comparison, the cycles are generalized in terms of}{The cycles presented are generalized in order to draw a more direct comparison. The generalized parameters include} isentropic efficiencies, heat exchanger approach temperatures, pressures, heat input, and pump constants. These values are summarized in Table \ref{tab-cycle-constants}.

\begin{specialtable}[htbp] 
    \mw{Also changing the specialtable position to allow latex to better place tables.}

    \caption{Constant cycle parameters with definition, variable and set value. \label{tab-cycle-constants}}
    \begin{tabular}{L{0.5\linewidth}cc}
    \toprule
    \textbf{Parameter} & \textbf{Variable}	& \textbf{Design Point Value}\\
    \midrule
    \textit{Efficiencies}\\
    Main Compressor & $\eta_{MC}$		& 0.91 (-)\\
    Re-Compressor & $\eta_{RC}$		& 0.89 (-)\\
    Turbine & $\eta_{T}$		& 0.90 (-)\\
    Pump & $\eta_{P}$      & 0.90 (-)\\
    \midrule
    \textit{Approach Temperatures}\\
    Low Temperature Recuperator & $\delta_{LTR}$		& 10 (K)\\
    High Temperature Recuperator & $\delta_{HTR}$		& 10 (K)\\
    Concentrating Solar Power Heat Exchanger & $\delta_{CSPHX}$	& 10 (K)\\
    \midrule
    \textit{Pressures}\\
    Pressure Ratio & $PR$ & 3.27 (-)\\
    High Side Pressure & $P_{2A}$ & 2.88e7 (Pa)\\
    \midrule
    \textit{Heat Into System}\\
    Lead-Cooled Fast Reactor Heat Transfer & $\dot{Q}_{LFRHX}$ & 9.5e8 (W)\\
    Concentrating Solar Power Heat Transfer & $\dot{Q}_{CSP}$ & 7.5e8 (W)\\
    \midrule
    \textit{Temperature}\\
    Main Compressor Inlet & $T_{1A}$ & 313.2 (K)\\
    %Lead-Cooled Fast Reactor sCO$_{2}$ Low Temperature & $T_{4}$,$T_{1C}$,$T_{5A}$,$T_{4C}$ & 673.2 (K)\\
    Lead-Cooled Fast Reactor sCO$_{2}$ High Temperature & $T_{5}$,$T_{2C}$,$T_{6A}$,$T_{5C}$ & 868.2 (K)\\
    \midrule
    \textit{Pumps}\\
    Pressure Rise Across Pump & $\Delta_{P}$ & 3.726e6 (Pa)\\
    Pump Low Side Pressure & $P_{S5-B}$ & 3.0e6 (Pa)\\ 
    \bottomrule
    \end{tabular}
\end{specialtable}

@@

In addition to generalized parameters, all cycles have identical recompression sides. The recompression side contains a PreCooler, Low Temperature Recuperator, and two compressors; Main Compressor and ReCompressor. \mw{components don't need to be capitalized -- they aren't proper nouns}

@@

\begin{specialtable}[H] 
    \caption{Summary of all modeled non-charging and charging cycles with descriptions. \label{tab-cycle_sum}}
    \begin{tabular}{lL{0.7\linewidth}}
    \toprule
    \textbf{Cycle Label} & \textbf{Description}\\
    \midrule
    \textit{Non-Charging}\\
    C-LFR-ON & Two-cycle configuration with LFR as heat source.\\
    C-CSP-ON & Two-cycle configuration with CSP as heat source.\\
    C-1HTR1T-ON & CSP and LFR heat sources in parallel with one turbine.\\
    C-2HTR3T-ON & Seperatre CSP and LFR loops each with dedicated HTR and turbine.\\
    \midrule
    \textit{Charging}\\
    C-LFR-PRE & Turbine is prior to the SALT HX.\\
    C-LFR-POST & Turbine is after the SALT HX.\\
    C-LFR-PAR & Turbine is parallel to the SALT HX.\\
    C-LFR-CIRC & Circulator bridges the LFR and SALT HX.\\
    \bottomrule
    \end{tabular}
\end{specialtable}

@@

The numerator in Equation \ref{eq-eta-cycle} is the \replaced{alternator}{Alternator} power, or the power produced from the turbines, $\dot{W}_{T}$, minus the required power of the compressors, $\dot{W}_{MC}$ and $\dot{W}_{RC}$. The denominator is the total power input into the system from the LFR HX, $\dot{Q}_{LFRHX}$, and CSP HX, $\dot{Q}_{CSPHX}$.

@@

The two-cycle configuration that is tested has independent sCO$_{2}$ loops \replaced{that share a common}{bridged by a} CSP cycle. This cycle has two sCO$_{2}$ Brayton Cycles: C-LFR-ON and C-CSP-ON. Configuration of components for these two cycles is identical with the exception of heat inputs. C-LFR-ON has heat provided from a LFR while C-CSP-ON has heat provided from the CSP. These two cycles individually operate when the focus of plant operation is primarily electricity generation.

The cycle that is using the LFR heat input in the two-cycle configuration is labeled as C-LFR-ON and the cycle diagram is illustrated in Figure \ref{c-lfr-on}. \mw{There are lots of little 1-2 sentence ``paragraphs'' that could be consolidated with some thought.}

\end{paracol}
\begin{figure}[!h] 
    \widefigure
    \includegraphics[width=\linewidth]{Definitions/c-lfr-on.pdf}
    \caption{Diagram for C-LFR-ON with focus on electricity generation\label{c-lfr-on}}
\end{figure}
\begin{paracol}{2}
\linenumbers
\switchcolumn

Two separate sensitivity studies on the LFR inlet temperature are completed for C-LFR-ON. The unconstrained study is performed by gradually increasing the mass flow to the main compressor while maximizing cycle efficiency. The constrained study is calculated by setting the LFR inlet temperature to the design value of 673.2 K (400$^{\circ}$C), which is a requirement of the LFR primary circuit to maximize power output within material limits.
\bl{flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint}
% 
The cycle that is using the CSP heat input in the two-cycle configuration is labeled C-CSP-ON and the cycle diagram is shown in Figure \ref{c-csp-on}.

\end{paracol}
\begin{figure}[!h] 
    \widefigure
    \includegraphics[width=\linewidth]{Definitions/c-csp-on.pdf}
    \caption{Diagram for C-CSP-ON with focus on electricity generation\label{c-csp-on}}
\end{figure}
\begin{paracol}{2}
\linenumbers
\switchcolumn

@@

\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from}
\mw{After lots of tinkering, I've not solved how to get the figures to avoid spilling over the edge of the page. I think it's a problem with the MDPI template. The figures have a lot of whitespace between components and numbers, and you may need to try to compress some of them down to make them more compact.}
\end{paracol}

\begin{figure}[H] 
    \widefigure
    \includegraphics[width=\linewidth]{Definitions/c-1htr1t-on.pdf}
    \caption{Diagram for C-1HTR1T-ON with focus on electricity generation\label{c-1htr1t-on}}
\end{figure}

\begin{paracol}{2}
\linenumbers
\switchcolumn

In this cycle, the LFR HX and CSP HX have identical inlet temperatures due to splitting the flow prior to their parallel orientation. Therefore, three sensitivity studies are done on the C-1HTR1T-ON EES model. The initial two studies have the low LFR temperature constrained to the value of 673.2 K with varied cold CSP TES \mw{varied cold CSP TES ... what? temperature?} and maximized cycle efficiency. \mw{State what variable(s) are manipulated in order to maximize cycle efficiency} \replaced{Two cold CSP TES temperature values are tested (683.2 K and 713.2 K)}{The two tested values for cold CSP TES} with constrained LFR low temperature\deleted{ are 683.2 K and 713.2 K}. The desired cold CSP TES temperature of 663.2 K is not possible with the constraint on the LFR low temperature (because it cannot be colder than the sCO$_2$ that removes heat from the salt). In this case, to obtain the desired cold CSP TES temperature, the constraint on the LFR low temperature is removed, dropping the temperature of the LFR inlet to 653.2 K. 
\bl{I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets. Asp you will want to explain the criteria that go into cold storage temp. Lower = more delta T = more dispatchability}

@@

Mixing two different temperature flows before the turbine in a Brayton cycle has a negative effect on cycle efficiency \mw{compared to...?}. To quantify the reduction in cycle efficiency, another cycle with no mixing prior to the turbine is desired. This cycle, C-2HTR3T-ON, can be seen in Figure \ref{c-2htr3t-on} and has two high temperature recuperators and three turbines. The LFR is powering one turbine, T1, and recuperating heat through a dedicated high temperature recuperator, HTR1. \mw{The LFR doesn't recuperate heat. Clarify what you mean here.} The CSP cycle \mw{CSP cycle refers to the salt loop. Here we mean something else.} also contains two separate turbines, T2, while having a dedicated high temperature recuperator, HTR2. \mw{Need to explain how T2 is actually 2 separate turbines represented diagramatically as 1, and why we can model it this way.} After the high temperature recuperators, the two flows are combined and sent to the LTR hot side. 
\bl{this is more about having a compromise option of intermediate complexity and efficiency}

@@

Three sensitivity studies are done on the C-2HTR3T-ON model -- two with the LFR low temperature constrained and one without this constraint. The two constrained studies had varied\mw{present tense} cold CSP TES temperature with the lowest temperature of 663.2 K and highest temperature of 713.2 K. The unconstrained low LFR inlet study is calculated at a cold CSP TES temperature of 663.2 K.  
\bl{this is clearer than the previous one but bullets could still be useful}

@@

Charging cycle configurations \replaced{accommodate}{focus on an} energy storage \replaced{modes of operation}{operating mode}. These configurations \replaced{examine the}{test the optimal} location of LFR heat extraction \replaced{via}{through} the SALT HX. To maximize the available heat for extraction, alternator \added{net} power is set to zero\added{, therefore requiring that the} turbine power is \deleted{therefore} equal to the compressors' demand. The excess energy from the LFR is thermally stored in the TES for later use when grid demand increases. \replaced{The location of heat extraction}{Comparison of where thermal energy is extracted} in the cycle is \replaced{compared within the C-LFR-ON Brayton cycle by placing}{done by using the same Brayton cycle, C-LFR-ON, and configuring} the salt heat exchanger in different locations around the turbine. To quantify the effectiveness of TES charging techniques a heat storage efficiency, \added{we define the metric} $\eta_{heatstorage}$ \deleted{, is defined by} in Equation \ref{eq-eta-heatstorage}.
\bl{explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output}

@@

Whereas $\dot{Q}_{S2C}$ is the amount of heat transferred through S2C and the addition of $\dot{Q}_{LFRHX}$ and $\dot{Q}_{CSPHX}$ is the total amount of heat input into the system from the LFR HX and CSP HX. \mw{not a full sentence}
